%============================================================================%
%	EXPERIENCE MODULE
%============================================================================%

%----------- EXPERIENCE -----------
\section{Experience}
\sectionListStart

\companyNameAndLocationHeading
{Protium Finance Limited}{Bangalore, KA}

\titleAndDateHeading
{Senior DevOps Engineer}{August 2022 \textbf{--} Present}
\outerBulletListStart
\bulletItem{Led a \textbf{4-engineer platform team} owning \textbf{cloud infrastructure, CI/CD, and production reliability}, defining architectural standards adopted across engineering teams.}
\bulletItem{Architected and delivered an \textbf{RBI-compliant internal GenAI platform} using \textbf{OpenWebUI, LiteLLM, and Azure}, enabling secure enterprise LLM adoption while enforcing auditability and data isolation controls.}
\bulletItem{Architecting an \textbf{AI-driven developer platform} leveraging a \textbf{code knowledge graph} to power automated \textbf{blast-radius analysis}, vulnerability remediation, and intelligent merge request validation across codebases.}
\bulletItem{Implemented \textbf{zero-trust access} using \textbf{HashiCorp Vault \& Boundary}, eliminating static credentials and reducing privileged access risk across production environments.}
\bulletItem{Reduced \textbf{Kubernetes compute spend by 45\%} by migrating production workloads from ASG-based nodes to \textbf{Karpenter autoscaling on EKS}, improving resource utilization and scaling efficiency.}
\bulletItem{Built an \textbf{organization-wide observability platform} (metrics, logs, profiling) using \textbf{Grafana, Mimir, Loki, Pyroscope, and OpenTelemetry}, enabling faster RCA and reducing incident diagnosis time.}
\bulletItem{Developed \textbf{centralized uptime monitoring and OnCall alerting workflows}, improving incident response readiness and production visibility across services.}
\bulletItem{Designed and standardized \textbf{reusable GitLab CI/CD pipeline templates}, onboarding microservices and Helm-based projects onto a unified delivery workflow, reducing deployment variability and improving developer release velocity.}
\bulletItem{Strengthened security posture by remediating \textbf{VAPT findings} and integrating centralized \textbf{SIEM monitoring with Microsoft Sentinel} for threat detection and audit readiness.}
\bulletItem{Integrated \textbf{SonarQube quality gates} into CI/CD pipelines, enforcing automated code quality and security checks prior to production deployments.}
\bulletItem{Led migration to \textbf{Terraform-based Infrastructure as Code}, replacing manual provisioning and standardizing deployments while accelerating environment provisioning.}
\bulletItem{Introduced \textbf{chaos engineering practices} using \textbf{ChaosToolkit} to automate disaster recovery drills and validate system resilience under failure scenarios.}
\outerBulletListEnd

\companyNameAndLocationHeading
{Tata Consultancy Services}{Chennai, TN}

\titleAndDateHeading
{System Engineer - DevOps}{August 2021 \textbf{--} July 2022}
\outerBulletListStart
\bulletItem{Automated infrastructure configuration using \textbf{Puppet} integrated with \textbf{CI/CD pipelines}, improving consistency of application and environment deployments.}
\bulletItem{Managed VM infrastructure lifecycle (provisioning, patching, decommissioning) while introducing standardized deployment workflows.}
\outerBulletListEnd

\titleAndDateHeading
{Assistant System Engineer}{August 2020 \textbf{--} July 2021}
\outerBulletListStart
\bulletItem{Developed and maintained \textbf{Puppet manifests} and Hiera configurations to support scalable environment provisioning.}
\bulletItem{Supported \textbf{MySQL} migration and upgrade initiatives in collaboration with database engineering teams.}
\outerBulletListEnd

\sectionListEnd