%============================================================================%
%	HEADER
%============================================================================%
\fcolorbox{white}{darkcol}{\begin{minipage}[c][2.5cm][c]{1\mpwidth}
	\begin {center}
		\HUGE{ \textbf{ \textcolor{white}{ \uppercase{ Venkatesh SM } } } } \\[-24pt]
		\textcolor{white}{ \rule{0.1\textwidth}{1.25pt} } \\[4pt]
		\large{ \textcolor{white} {Senior DevOps Engineer} }
	\end {center}
\end{minipage}} \\[14pt]
\vspace{-12pt}

%============================================================================%
%	OBJECTIVES Section
%============================================================================%
\rsection{OBJECTIVE}

\rtext{Results-driven DevOps professional with extensive experience in cloud infrastructure, CI/CD pipelines, and automation. 
Aiming to leverage my expertise in AWS, Kubernetes, and infrastructure as code to optimize deployment processes and 
enhance system reliability in a challenging DevOps leadership role.}

%============================================================================%
%	WORK EXPERIENCE Section
%============================================================================%
\rsection{WORK EXPERIENCE}

\revent
	{2025 - Present}
	{Associate Vice President - DevOps}
	{Protium Finance Limited}
	{Led platform, cost and security programs across multi-account AWS and Kubernetes; drove modernization, resilience and developer productivity.}
	{\rlist{
		\item Built observability with \textbf{Grafana}, \textbf{Mimir}, \textbf{Loki}, \textbf{Pyroscope}, \textbf{Alloy (OTel)}.
		\item Standardized \textbf{metrics, logs, traces}; defined \textbf{SLOs} and on-call.
		\item Added \textbf{uptime monitoring} via ingress auto-discovery.
		\item Migrated from EKS ASG to \textbf{Karpenter}; improved \textbf{bin-packing} and scale-to-zero.
		\item Delivered \textbf{double-digit} compute \textbf{cost reduction}.
		\item Replaced static DB creds with \textbf{Vault + Boundary}; short-lived, \textbf{audited} access.
		\item Centralized security telemetry: \textbf{WAF}, \textbf{CloudTrail}, \textbf{ALB/NLB} → \textbf{OpenSearch} + \textbf{Microsoft Sentinel} (SIEM).
		\item Remediated \textbf{VAPT} issues: \textbf{open redirect (host header)}, \textbf{Keycloak XSS}, \textbf{password reset poisoning}, \textbf{missing CSP}, \textbf{rate limiting}, \textbf{DMARC}.
		\item Delivered \textbf{GenAI} platform (RBI-compliant) with \textbf{OpenWebUI} + \textbf{LiteLLM}.
		\item Added AI-assisted profiling in \textbf{Pyroscope} to surface performance bottlenecks.
		\item Deployed \textbf{Azure} document-intelligence with \textbf{Terraform} + CI/CD (train → prod).
		\item Ran \textbf{DR drills} using \textbf{ChaosToolkit}; automated failure injection and validations.
		\item Converted components to \textbf{EKS managed add-ons}; executed zero/low-downtime upgrades (\textbf{PostgreSQL, Redis, Elasticsearch, Keycloak, Metabase, SonarQube, Vault/Boundary}).
		\item Scaled developer self-service with \textbf{Backstage} and golden paths.
		\item Cost governance: \textbf{GP2→GP3}, \textbf{rightsizing}, \textbf{CloudWatch metrics pruning}, \textbf{VPA recommender}.
	}}
	{\rlist {
		\item AWS (EKS, EC2, EBS GP3, CloudWatch/CloudTrail, WAF, ALB/NLB), Kubernetes, Helm, Karpenter, VPA, Ingress, Terraform
		\item Grafana Stack (Grafana, Mimir, Loki, Pyroscope, Alloy/OTel), OpenSearch, Microsoft Sentinel, HashiCorp Vault/Boundary, Backstage, ChaosToolkit, SonarQube, Azure (AI)
	}}

\revent
	{2022 - 2025}
	{Senior DevOps Engineer}
	{Protium Finance Limited}
	{Owned EKS-first platform delivery; migrated workloads to Kubernetes; established CI/CD, observability and security foundations while optimizing cost.}
	{\rlist{
		\item Migrated Docker workloads to \textbf{AWS EKS} with zero/low downtime.
		\item Designed \textbf{multi-environment} clusters, \textbf{ingress} strategy and \textbf{metrics-server}.
		\item Implemented CI/CD (\textbf{Jenkins/GitLab CI}) with \textbf{SonarQube} quality gates.
		\item Standardized \textbf{Helm charts} and \textbf{Terraform} IaC.
		\item Bootstrapped observability: \textbf{Grafana}, \textbf{Loki}, \textbf{Mimir}, \textbf{Pyroscope}.
		\item Enabled dev \textbf{OpenTelemetry} metrics via agent autodiscovery.
		\item Introduced \textbf{SLO} alerts and on-call workflows.
		\item Logging pipelines to \textbf{OpenSearch}; enabled \textbf{WAF} and \textbf{CloudTrail} baselines.
		\item Automated EC2 patching with \textbf{AWS SSM}; hardened base AMIs.
		\item Cost savings: \textbf{GP2→GP3}, \textbf{metrics pruning}, \textbf{rightsizing/decommissioning}.
		\item Codified manual resources in \textbf{Terraform} modules.
		\item Hosted \textbf{Frappe CRM} on EKS; productionized backing services and observability.
	}}
	{\rlist {
		\item Kubernetes, AWS EKS, Helm, Terraform, Jenkins/GitLab CI, SonarQube, OpenTelemetry, Metrics Server
		\item AWS (EC2, EBS, CloudWatch, CloudTrail, WAF, SSM), OpenSearch, Grafana, Loki, Mimir, Pyroscope
	}}

\revent
	{2020 - 2022}
	{DevOps Engineer}
	{Tata Consultancy Services}
	{Supported mortgage platform \textbf{CI/CD} and infrastructure; integrated \textbf{Puppet} and \textbf{Salesforce} into automated delivery. 
	Owned environment configuration, release orchestration and production deployments.}
	{\rlist{
		\item Server \textbf{build/patch/decommission} and configuration management.
		\item Built \textbf{Jenkins} pipelines for repeatable application releases.
		\item Authored \textbf{Puppet} manifests for standardized deployments.
		\item Automated \textbf{Puppet Hiera} updates via \textbf{Jenkins} + shell scripts.
	}}
	{\rlist {
		\item \textbf{Jenkins}, \textbf{Puppet}, \textbf{Git}, Bitbucket, Nexus
		\item Red Hat, Debian (Ubuntu), Unix shell
	}}


%============================================================================%
%	PERSONAL PROJECTS Section
%============================================================================%
\rsection{PERSONAL PROJECTS}

	\revent
	{2022}
	{\iconhrefexternal{ExternalLink}{9}{Infra}{https://github.com/venkivijay/infra}{black}}
	{Configuration management using Ansible}
	{Ansible playbook to configure my workstation and servers from scratch
	}
	{\rlist{
		\item Utilizes ansible-pull and cron to configure/maintain my systems
		\item Powerful enough to duplicate my workstation with a single command
		\item Patches system, installs packages, creates users, configures system settings
		\item Sets up Jenkins flawlessly on my server
	}}
	{\rlist {
		\item Ansible, Shell, Jinja
	}}

	\revent
	{2022}
	{\iconhrefexternal{ExternalLink}{9}{Resume}{https://github.com/venkivijay/resume}{black}}
	{Version controlled resume}
	{The resume you are viewing right now is this project.
	}
	{\rlist{
		\item Resume as code and can be version controlled
		\item Built using TeX
		\item Build and deploy to gh-pages on code merge
		\item One resume link to share anywhere which will always be upto date
	}}
	{\rlist {
		\item TeX - LaTeX, GitHub Actions, YAML
	}}